Secure Composition of Robust and Optimising Compilers

### 2023-06-14 popl/main.tex
Typo fix

\begin{definition}[\glsfirst{sms}]\label{def:trace:smsdef}
  A trace $\trace$ is spatial memory safe ($\trace\in\smssafe$) iff given $\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ m;\sandboxtag';\securitytag'}$, then $n<m$.
\end{definition}

>>>>

\begin{definition}[\glsfirst{sms}]\label{def:trace:smsdef}
  A trace $\trace$ is spatial memory safe ($\trace\in\smssafe$) iff given $\ev{Alloc\ \loc\ m;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ n;\sandboxtag';\securitytag'}$, then $n<m$.
\end{definition}
